---
title: "Health Care in United State(US)"
output: 
  html_notebook: 
    toc: true
    fig_caption: true
---

This is an analysed data of health care accessed in the US from 2019 till present.

Disclaimer: This analysis should not be used in decision making or any sort as the data used is not comprehensive to inform any decision.

#### Comprehensive data set.

```{r Comprehensive data set}

Healthcare_dataset_frame <- read.csv("healthcare_dataset.csv")
Healthcare_dataset_frame
```

```{r Data summary.1}

summary(Healthcare_dataset_frame)
print(summary)
```

#### Data wrangling.

```{r Wrangling data for analysis}

Healthcare_dataset <- Healthcare_dataset_frame[1:55500, c("Age","Gender","Blood.Type","Medical.Condition","Date.of.Admission","Insurance.Provider","Billing.Amount","Admission.Type","Discharge.Date","Medication","Test.Results")]
Healthcare_dataset
```

```{r Proper data type}

Preprocess_Healthcare_dataset <- function(Healthcare_dataset, src_Healthcare_dataset) {
    
    Healthcare_dataset$Age <- as.factor(Healthcare_dataset$Age)
    Healthcare_dataset$Gender <- as.factor(Healthcare_dataset$Gender)
    Healthcare_dataset$'Blood.Type' <- as.factor(Healthcare_dataset$'Blood.Type')
    Healthcare_dataset$'Medical.Condition' <- as.factor(Healthcare_dataset$'Medical.Condition')
    Healthcare_dataset$'Date.of.Admission' <- as.Date(Healthcare_dataset$'Date.of.Admission')
    Healthcare_dataset$'Insurance.Provider' <- as.factor(Healthcare_dataset$'Insurance.Provider')
    Healthcare_dataset$'Billing.Amount' <- as.numeric(gsub(",","",Healthcare_dataset$'Billing.Amount'))
    Healthcare_dataset$'Admission.Type' <- as.factor(Healthcare_dataset$'Admission.Type')
    Healthcare_dataset$'Discharge.Date' <- as.Date(Healthcare_dataset$'Discharge.Date')
    Healthcare_dataset$'Test.Results' <- as.factor(Healthcare_dataset$'Test.Results')
    return(Healthcare_dataset)
}
Preprocess_Healthcare_dataset(Healthcare_dataset, src_Healthcare_dataset)
```

```{r Data summary.2}

processed_healthcare_dataset <- Preprocess_Healthcare_dataset(Healthcare_dataset, src_Healthcare_dataset)
summary(processed_healthcare_dataset)
print(summary)
```

#### Analysis 1 (Age Category against Gender).3.0.

```{r Analysis of Age Category and Gender.1.0}

# Data extraction, sorting & adding Age Category
# The different age categories include:
# Children = 0 - 14 years.
# Youth = 15 - 24 years.
# Adult = 25 - 64 years.
# Seniors = 65 years and older.

GenderandAge_dataset <- processed_healthcare_dataset[1:55500, c("Age","Gender")]
Sorted_GenderandAge_dataset <- function(GenderandAge_dataset, src_GenderandAge_dataset) {
  
  GenderandAge_dataset$Age <- sort(GenderandAge_dataset$Age, decreasing = FALSE)
  
  GenderandAge_dataset$Age <- as.numeric(as.character(GenderandAge_dataset$Age))
  
  breaks <- c(-Inf, 14, 24, 64, Inf)
  labels <- c("Children", "Youth", "Adults", "Seniors")
  GenderandAge_dataset$'Age.Category' <- cut(GenderandAge_dataset$Age, breaks = breaks, labels = labels, right = TRUE)
  
  GenderandAge_dataset$Age <- as.factor(as.character(GenderandAge_dataset$Age))
  
  return(GenderandAge_dataset)
  
}

Sorted_GenderandAge_dataset <- Sorted_GenderandAge_dataset(GenderandAge_dataset, src_GenderandAge_dataset)
Sorted_GenderandAge_dataset
```

```{r Data summary.3}

summary(Sorted_GenderandAge_dataset)
print(summary)
```

```{r Subsetting the different age categories}
# Extract rows where Age.Category is "Children" and Gender is either "Male" or "Female"
children_gender_subset <- subset(Sorted_GenderandAge_dataset, Age.Category == "Children" & (Gender == "Male" | Gender == "Female"))
print(children_gender_subset)

# Extract rows where Age.Category is "Youth" and Gender is either "Male" or "Female"
youth_gender_subset <- subset(Sorted_GenderandAge_dataset, Age.Category == "Youth" & (Gender == "Male" | Gender == "Female"))
print(youth_gender_subset)

# Extract rows where Age.Category is "Adults" and Gender is either "Male" or "Female"
adults_gender_subset <- subset(Sorted_GenderandAge_dataset, Age.Category == "Adults" & (Gender == "Male" | Gender == "Female"))
print(adults_gender_subset)

# Extract rows where Age.Category is "Seniors" and Gender is either "Male" or "Female"
seniors_gender_subset <- subset(Sorted_GenderandAge_dataset, Age.Category == "Seniors" & (Gender == "Male" | Gender == "Female"))
print(seniors_gender_subset)

```

```{r Data summary.4}
summary(children_gender_subset)
print(summary)

summary(youth_gender_subset)
print(summary)

summary(adults_gender_subset)
print(summary)

summary(seniors_gender_subset)
print(summary)
```

| ***Age.Category***   | ***Female*** | ***Male*** |
|----------------------|--------------|------------|
| Children (\<=14 yrs) | 21           | 11         |
| Youth (15 - 24 yrs)  | 2828         | 2849       |
| Adults (25 - 64 yrs) | 16457        | 16247      |
| Seniors ( \>=65 yrs) | 8420         | 8667       |

: [***Healthcare Access Between Both Genders Across the Different Age Categories***]{.underline}

```{r Table, Healthcare Access Among Both Genders and Age Group.}

AgeCategory_Gender_Analysis_dataframe <- data.frame(
  Age.Category = c('Children (<=14 yrs)', 'Youth (15 - 24 yrs)', 'Adults (25 - 64 yrs)', 'Seniors ( >=65 yrs)'),
  Female = c(21, 2828, 16457, 8420),
  Male = c(11, 2849, 16247, 8667)
)
AgeCategory_Gender_Analysis_dataframe
```

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
