---
title: "Health Care in United State(US)"
output: html_notebook
---

`This is an analysed data of health care accessed in US from 2019 till present. This analysis should not be used in decision making or any sort as the data used is not comprehensive to inform any decision.`

#### Comprehensive data set.

```{r}
Healthcare_dataset_frame <- read.csv("healthcare_dataset.csv")
Healthcare_dataset_frame
```

```{r}
# Data summary
summary(Healthcare_dataset_frame)
print(summary)
```

#### Data wrangling.

```{r}
# Wrangling data for analysis
Healthcare_dataset <- Healthcare_dataset_frame[1:55500, c("Age","Gender","Blood.Type","Medical.Condition","Date.of.Admission","Insurance.Provider","Billing.Amount","Admission.Type","Discharge.Date","Medication","Test.Results")]
Healthcare_dataset
```

```{r}
# Proper data type
Preprocess_Healthcare_dataset <- function(Healthcare_dataset, src_Healthcare_dataset) {
    
    Healthcare_dataset$Age <- as.factor(Healthcare_dataset$Age)
    Healthcare_dataset$Gender <- as.factor(Healthcare_dataset$Gender)
    Healthcare_dataset$'Blood.Type' <- as.factor(Healthcare_dataset$'Blood.Type')
    Healthcare_dataset$'Medical.Condition' <- as.factor(Healthcare_dataset$'Medical.Condition')
    Healthcare_dataset$'Date.of.Admission' <- as.Date(Healthcare_dataset$'Date.of.Admission')
    Healthcare_dataset$'Insurance.Provider' <- as.factor(Healthcare_dataset$'Insurance.Provider')
    Healthcare_dataset$'Billing.Amount' <- as.numeric(gsub(",","",Healthcare_dataset$'Billing.Amount'))
    Healthcare_dataset$'Admission.Type' <- as.factor(Healthcare_dataset$'Admission.Type')
    Healthcare_dataset$'Discharge.Date' <- as.Date(Healthcare_dataset$'Discharge.Date')
    Healthcare_dataset$'Test.Results' <- as.factor(Healthcare_dataset$'Test.Results')
    return(Healthcare_dataset)
}
Preprocess_Healthcare_dataset(Healthcare_dataset)
```

```{r}
# Data summary
processed_healthcare_dataset <- Preprocess_Healthcare_dataset(Healthcare_dataset)
summary(processed_healthcare_dataset)
print(summary)
```

#### Analysis.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
